Vision and Cognitive Systems Final Project

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper

\section{Related Works}
To remove camera noise but maintains the contours a  Bilateral filter\cite{b1} is used.
OTSU\cite{b2} is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
Opencv Find Counturs\cite{b3} function is been used to find counturs in a previouslly modified frame in order to detect painting
The functions approxPolyDP\cite{b4} approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision. It uses the Douglas-Peucker algorithm  
ORB\cite{b5} is a feature detection algorithm like SIFT while being almost two orders of magnitude faster.
YoloV3 \cite{b5}  is a famous neural network for fast object detection that will be used in this paper for people detection.\\

@@

\section{People Detection}
A neural network (YoloV3) is used for people detection.\\
At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class \ref{fig_People_detection} .\\

@@

@@

\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} \url{https://docs.opencv.org/2.4/modules/imgproc/doc/structural_analysis_and_shape_descriptors.html#approxpolydp}
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\bibitem{b7}Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b8} \url{https://docs.python.org/3/library/pickle.html}
\bibitem{b9} Lowe, David G. "Distinctive image features from scale-invariant keypoints." International journal of computer vision 60.2 (2004): 91-110.
\bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.

>>>>

\section{Related Works}
To remove camera noise but maintains the contours a  Bilateral filter\cite{b1} is used.
OTSU\cite{b2} is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
Opencv Find Counturs\cite{b3} function is been used to find counturs in a previouslly modified frame in order to detect painting
The functions approxPolyDP\cite{b4} approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision. It uses the Douglas-Peucker algorithm  
ORB\cite{b5} is a feature detection algorithm like SIFT while being almost two orders of magnitude faster.
YoloV3 \cite{b5}  is a famous neural network for fast object detection that will be used in this paper for people detection.\\
A graphical user interfaces has been created to show the work and process automatically the video using tkinter \cite{b12}

@@

\section{People Detection}
A neural network (YoloV3) is used for people detection.\\
At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
The weights for the network are obtained from an already trained network on COCO \cite{b11}, a famous dataset containing 80 different classes.\\
In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class \ref{fig_People_detection} .\\

@@

\section{GUI}
A graphical user interface has been created using tkinter library \cite{b12} to show in real time what our program is doing. It’s also capable to process new video simply by typing its name into the input field.
Two different threads run at the same time, one for the gui and the other one for our pipeline.
After a complete analysis, a new video is created showing what the interface has displayed for the entire time of its utilization.

@@

\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} \url{https://docs.opencv.org/2.4/modules/imgproc/doc/structural_analysis_and_shape_descriptors.html#approxpolydp}
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\bibitem{b7}Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b8} \url{https://docs.python.org/3/library/pickle.html}
\bibitem{b9} Lowe, David G. "Distinctive image features from scale-invariant keypoints." International journal of computer vision 60.2 (2004): 91-110.
\bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.
\bibitem{b11}Lin TY. et al. (2014) Microsoft COCO: Common Objects in Context. In: Fleet D., Pajdla T., Schiele B., Tuytelaars T. (eds) Computer Vision – ECCV 2014. ECCV 2014. Lecture Notes in Computer Science, vol 8693. Springer, Cham
\bibitem{b12} \url{https://docs.python.org/3/library/tkinter.html}
